%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{select courses}

\begin{entrylist}
%------------------------------------------------
\entry
  {2008\\\faChevronDown\\2010}
  {Fundamentals of Power Electronics: Power Electronics I \& II, Power Electronics (M.Sc.), Switching Power Converters (M.Sc.), Power System Design (M.Sc.), Electro-Magnetic Compatibility (M.Sc.)}
  {Queen's University \& Royal Military College of Canada}
  {Switching devices, switching converters (AC-to-DC, DC-to-DC, DC-to-AC), 
  loss-less switching (zero-voltage switching, zero-current switching) resonant converters, soft-switching converters. 
  Variable frequency control, phase-shift and hybrid control. Small signal 
  models, large signal models, peak current mode and average current mode control, system stability issues, 
  digital control techniques, fuzzy logic control, sliding mode control, and non-linear control strategies. 
  Electro-magnetic interference, EM compatibility, crosstalk, HF circuits.}
%------------------------------------------------
\entry
  {2008\\\faChevronDown\\2013}
  {Robotics and Control: Introduction to Robotics, Control Systems (4th Year), Control of Mobile Robotics (2013)}
  {\\Queen's University \& Coursera}
  {Rigid body kinematics, manipulator kinematics, workspace, singularity, redundancy, 
  manipulator dynamics, and trajectory generation. Herd navigation and cooperation, aerial multirotor control with disturbance
  mitigation, and bipedal locomotion. Linear systems and feedback control, time-domain specifications, 
  PID control, steady-state error and disturbance rejection, and state-space analysis.}
%------------------------------------------------
\entry
  {2005\\\faChevronDown\\2009}
  {Software Engineering, Data Structures, Database Management Systems, Computer Graphics, Computer Architecture I/II, Microprocessor Systems, Modelling \& Systems Simulation, Cryptography I}
  {\\Queen's University \& Coursera}
  {Software engineering concepts, data structures: lists, stacks, queues, trees, graphs. Algorithms: sorting, searching. Abstract data types, modules, interfaces, and specifications.
  Computer structures, instruction set architecture. Assembly language programming. Memory hierarchy, I/O, and interrupts. Pipelining and parallelism.
  Performance evaluation of computer systems and networks through simulation. System security.}
%------------------------------------------------
\end{entrylist}