% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Jonathan}{Mash}           % Your name
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}
15 Windfield Cres
Kingston, ON, K7K 6G3
Canada
~
+1 (613)-329-0825
~
me@jonmash.ca
%
\section{programming}
{\color{red} $\varheartsuit$} Node.JS
Javascript, HTML5, CSS3, C/C++, C\#, 
{\color{red} $\varheartsuit$} Git
%
\section{interests}
electronics, robotics, drones, solar/alternative energies
%
\end{aside}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{skills}
  \vspace{-0.2cm}

Project management, product development, product design. electronics design, embedded systems, prototyping, manufacturing.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {2010--Now}
  {SPARQ Systems}
  {Kingston, Ontario, Canada}
  {\jobtitle{Product Development Lead}
\begin{itemize}
\item Designed, prototyped, and manufactured a compact in-home device for solar panel monitoring. Involved in the design decisions of the associated web portal.
\item Developed novel communication protocol over Power Line Communication using FEC coding for robust monitoring and control of the microinverters.
\item Developed the manufacturing, assembly, and testing procedures to ensure only high quality products are delivered to our customers.
\item Trusted by senior management to provide independent engineering support to customers due to in-depth knowledge of the entire system.
\end{itemize}
}
%------------------------------------------------
\entry
  {2009--2013}
  {ePOWER--Centre for Energy and Power Electronics Research}
  {Kingston, Ontario, Canada}
  {\jobtitle{Engineering Research Assistant}
  \begin{itemize}
    \item Researched and designed a medium-power front-end converter for telecommunications equipment using simulation tools. 
    \item Developed a wind turbine emulator using an induction motor connected to a permanent magnet synchronous generator for use in research activities.
    \item Developed novel non-linear control strategies for PMSG connected wind turbine systems.
  \end{itemize}}
%------------------------------------------------
\entry
  {2004--2008}
  {Queen's University Solar Vehicle Tam}
  {Kingston, Ontario Canada}
  {\jobtitle{Project Manager}\\
  Competed at two international competitions:
  \begin{itemize}
    \item Panasonic World Solar Challenge, Australia (October 2007)
    \item North American Solar Challenge, USA and Canada (July 2005)
  \end{itemize}
  Responsibilities:
  \begin{itemize}
    \item Oversaw all aspects of a semi-professional racing team.
    \item Supervised the design, fabrication and testing of the vehicle.
    \item Directed efforts in: marketing, sponsorship, event planning, and PR.
    \item Managed financial planning, purchasing, cash flow, and budgeting.
    \item
  \end{itemize}
  Skills and Innovative Approaches:
  \begin{itemize}
    \item Reorganized the team structure to increase efficiency and improve communication flow.
    \item Led fundraising efforts, raising over \$500,000 worth of cash and donations.
    \item Knowledge of all vehicle design incl.: electrical, mechanical, and software.
    \item Designed and constructed a solar array producing over 1200 Watts.
    \item Team’s expert on power systems, lithium-based batteries, and solar cells.
  \end{itemize}
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2009--2013}
{M.Sc. {\normalfont in Electrical Engineering}}
{Queen's University @ Kingston}
{Queen’s Centre for Energy and Power Electronics Research--Dr. Praveen Jain\\
Course Average: 92\%}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2004--2009}
{B.Sc. {\normalfont in Electrical Engineering}}
{Queen's University @ Kingston}
{Ranked 2\textsuperscript{nd} of 45 students in Electrical Engineering.\\
Ranked 5\textsuperscript{th} of 576 students in all of Engineering.\\
Final Year Average: 93\%}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{other qualifications}

\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{Qualification}
{Institution}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2011}
{Qualification}
{Institution}
{\vspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Award name}
{Institution}
{Award description. Award description. Award description. Award description. Award description. Award description. Award description. }
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}
  \vspace{-0.2cm}

\textbf{professional:} professional interest 1, professional interest 2 and professional interest 3. \textbf{personal:} personal interest 1, personal interest 2, personal interest 3 and personal interest 4.

%----------------------------------------------------------------------------------------

\end{document}