%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {2010\\\faChevronDown\\{\bodyfontit present}}
  {SPARQ Systems}
  {Kingston, Ontario, Canada}
  {\jobtitle{Lead Product Developer}
\begin{itemize}[leftmargin=12pt]
	\item Given complete control over the design and implementation of an new monitoring platform developed using all new microinverter technology.
  \item Developed an in-house {\bodyfontit embedded Linux} device utilizing advanced {\bodyfontit Zigbee} communication, USB, 802.11 {\bodyfontit WiFi}, and a {\bodyfontit Websocket} API to connect to cloud servers.
  \item Built an Amazon {\bodyfontit Cloud} based monitoring and control solution based on {\bodyfontit Node.JS}, CouchDB {\bodyfontit NoSQL} database, and a modern {\bodyfontit HTML5} web front end.
	\item Actively involved in high-level market research, feature requirements derivation, and product requirements specifications.
	\item Component selection, {\bodyfontit PCB} design, aided mechanical design, produced and tested {\bodyfontit prototypes}, and oversaw the entire process from {\bodyfontit design} through to {\bodyfontit manufacturing}.
  \item Led and supported the deployment of field trials at sites across North America.
	\item Recruited and trained new employees to grow the group from just myself to a team of six highly talented developers and engineers.
	\item Coordinated multiple teams and external contractors working on key projects.
\end{itemize}
\jobtitle{Product Developer}
\begin{itemize}[leftmargin=12pt]
	\item Designed, prototyped, and manufactured an in-house embedded device for solar panel and inverter monitoring.
	\item Developed a novel Power Line Communication protocol using Forward Error Correcting codes for robust communication to the microinverters.
	\item Developed the manufacturing, assembly, and testing procedures to ensure high quality products are delivered to customers.
	\item Trusted by senior management to provide independent engineering support to customers because of my in-depth knowledge of the entire product line.
\end{itemize}
}
%------------------------------------------------
\entry
  {2009\\\faChevronDown\\2013}
  {Centre for Energy and Power Electronics Research}
  {Kingston, Ontario, Canada}
  {\jobtitle{Engineering Research Assistant}
  \begin{itemize}[leftmargin=12pt]
    \item Researched and designed a medium-power front-end converter for telecommunications equipment using simulation tools.
    \item Developed a wind turbine emulator using an induction motor connected to a permanent magnet synchronous generator for use in research activities.
    \item Derived novel non-linear control schemes for a PMSG-connected wind turbine.
  \end{itemize}}
%------------------------------------------------
\entry
  {2008}
  {Ontario Power Generation}
  {Pickering, Ontario, Canada}
  {\jobtitle{Student - Computers and Controls Division}
  \begin{itemize}[leftmargin=12pt]
    \item Developed and deployed an online portal to aid in knowledge retention.
    \item Identified project requirements, researched possible solutions, and implemented the chosen solution: Microsoft's Sharepoint and custom workflows.
  \end{itemize}
}
%------------------------------------------------
\entry
  {2004\\\faChevronDown\\2008}
  {Queen's University Solar Vehicle Team}
  {Kingston, Ontario, Canada}
  {\jobtitle{Project Manager}\\
  Competitions: {\bodyfontit World Solar Challenge Australia} \&
  {\bodyfontit North American Solar Challenge}
  \begin{itemize}[leftmargin=12pt]
    \item Oversaw all aspects of a semi-professional racing team.
    \item Supervised the design, fabrication and testing of the vehicle.
    \item Directed efforts in marketing, sponsorship, event planning, and PR.
    \item Managed all financial planning, purchasing, cash flow, and budgeting.
    \item Led fund-raising efforts, raising over \$500,000 in cash and in-kind donations.
    \item Knowledge of all vehicle design including electrical, mechanical, and software.
    \item Was the team’s expert on power systems, lithium-based batteries, and solar cells.
  \end{itemize}
}
%------------------------------------------------
\end{entrylist}