%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{other experience}
\begin{entrylist}
%------------------------------------------------
\entry
  {2010\\\faChevronDown\\2016}
  {SPARQ Systems}
  {Kingston, Ontario, Canada}
  {\jobtitle{Lead Product Developer}
  \begin{itemize}[leftmargin=12pt]
    \item Recruited and trained new employees to grow the group from just myself to a team of six highly talented developers and engineers.
    \item Actively involved in high-level market research, feature requirements derivation, and product requirements specifications.
    \item Developed an in-house embedded Linux device utilizing advanced Zigbee communication, USB, 802.11 WiFi, and a WebSocket API to connect to cloud servers.
    \item Built an AWS-based monitoring and control product using web technologies.
    \item Oversaw the entire hardware process from design through to manufacturing, including component selection, PCB design, mechanical design, prototyping, and testing. Developed manufacturing, assembly, and testing procedures to ensure that high quality products are delivered to customers.
    \item Led and supported the deployment of field trials at sites across North America.
    \item Coordinated multiple teams and external contractors working on key projects.
    \item Developed a novel Power Line Communication protocol using Forward Error Correcting codes for robust communication with solar microinverters.
\end{itemize}
}
%------------------------------------------------
\entry
  {2009\\\faChevronDown\\2013}
  {Centre for Energy and Power Electronics Research}
  {Kingston, Ontario, Canada}
  {\jobtitle{Engineering Research Assistant}
  \begin{itemize}[leftmargin=12pt]
    \item Researched and designed a medium-power front-end converter for telecommunications equipment using simulation tools.
    \item Developed a wind turbine emulator using an induction motor connected to a permanent magnet synchronous generator for use in research activities.
    \item Derived novel non-linear control schemes for a PMSG-connected wind turbine.
  \end{itemize}}
%------------------------------------------------
\entry
  {2008}
  {Ontario Power Generation}
  {Pickering, Ontario, Canada}
  {\jobtitle{Student - Computers and Controls Division}
  \begin{itemize}[leftmargin=12pt]
    \item Developed and deployed an online portal to aid in knowledge retention.
    \item Identified project requirements, researched possible solutions, and implemented the chosen solution: Microsoft's Sharepoint with custom workflows.
  \end{itemize}
}
%------------------------------------------------
\entry
  {2004\\\faChevronDown\\2008}
  {Queen's University Solar Vehicle Team}
  {Kingston, Ontario, Canada}
  {\jobtitle{Project Manager}\\
  Competitions: {\bodyfontit World Solar Challenge Australia} \&
  {\bodyfontit North American Solar Challenge}
  \begin{itemize}[leftmargin=12pt]
    \item Oversaw all aspects of a semi-professional racing team.
    \item Supervised the design, fabrication and testing of the vehicle.
    \item Directed efforts in marketing, sponsorship, event planning, and PR.
    \item Managed all financial planning, purchasing, cash flow, and budgeting.
    \item Led fund-raising efforts, raising over \$500,000 in cash and in-kind donations.
    \item Knowledge of all vehicle design including electrical, mechanical, and software.
    \item Was the team’s expert on power systems, lithium-based batteries, and solar cells.
  \end{itemize}
}
%------------------------------------------------
%\entry
%  {2007\\\faChevronDown\\2011}
%  {Faculty of Applied Science}
%  {Kingston, Ontario, Canada}
%  {\jobtitle{Senior Teaching Assistant}\\
%  {\headingfont Project Manager} - Managed and taught six teams of four students the process of design, implementation, and prototyping in a team environment.\\
%  {\headingfont Lab Manager} - Facilitated hardware and software labs in four undergraduate ECE courses. Assisted in the development and execution of a new robotics project-based course for second year ECE students.}
%------------------------------------------------
\end{entrylist}